Spike-and-Slab Generalized Additive Models and Scalable Algorithms for High-Dimensional Data

### 2022-03-21 Manuscript/Tabs/sim_time_tab.tex
Revise caption

\begin{sidewaystable}[!h]
\centering
\begin{tabular}{lrllllll}
  \hline
Distribution & P & mgcv & COSSO & Adaptive COSSO & BHAM & SB-GAM & spikeSlabGAM \\ 
  \hline
Binomial &   4 & 0.18 (0.04) & 3.16 (1.39) & 5.51 (4.07) & 2.73 (0.22) & 347.17 (89.43) & 8.41 (0.91) \\ 
  Binomial &  10 & 3.46 (11.06) & 8.30 (1.70) & 10.66 (5.30) & 4.08 (0.29) & 539.05 (135.55) & 20.36 (2.16) \\ 
  Binomial &  50 & 660.31 (141.53) & 103.41 (20.00) & 118.82 (18.45) & 14.22 (0.58) & 1590.09 (142.19) & 236.73 (14.83) \\ 
  Binomial & 100 & - & 662.61 (125.00) & 672.65 (185.09) & 31.61 (2.56) & 2720.53 (250.43) & 967.97 (186.85) \\ 
  Binomial & 200 & - & 5325.66 (995.60) & 4963.93 (1482.11) & 82.17 (3.29) & 4788.76 (420.64) & 3371.88 (194.02) \\ 
  Gaussian &   4 & 0.05 (0.01) & 0.75 (0.09) & 0.75 (0.11) & 8.78 (1.57) & 38.82 (2.74) & 1.84 (0.18) \\ 
  Gaussian &  10 & 0.32 (0.39) & 3.42 (0.24) & 3.41 (0.23) & 20.77 (3.95) & 76.12 (5.55) & 5.93 (0.57) \\ 
  Gaussian &  50 & 72.03 (57.99) & 33.98 (2.88) & 34.35 (2.86) & 285.73 (12.53) & 374.76 (23.79) & 65.18 (8.12) \\ 
  Gaussian & 100 & - & 117.79 (3.33) & 119.63 (3.66) & 372.01 (56.92) & 640.44 (21.91) & 194.14 (8.09) \\ 
  Gaussian & 200 & - & 518.86 (40.78) & 524.76 (39.15) & 471.46 (72.23) & 1300.70 (72.74) & 738.52 (62.76) \\ 
   \hline
\end{tabular}
\caption{The average and standard deviation of computation time in seconds,
      including cross-validation and final model fitting, over 50 iterations. The models
      of comparison include the proposed Bayesian hierarchical additive model (BHAM) fitted
      with Iterative Weighted Least Square (BHAM-IWLS) and Coordinate Descent (BHAM-CD)
      algorithms, component selection and smoothing operator (COSSO), adaptive COSSO,
      mgcv and sparse Bayesian generalized additive model (SB-GAM). mgcv doesn't 
      provide estimation whe number of parameters exceeds sample size i.e. p = 100, 200.} 
\label{tab:time_sim}
\end{sidewaystable}

>>>>

\begin{sidewaystable}[!h]
\centering
\begin{tabular}{lrllllll}
  \hline
Distribution & P & mgcv & COSSO & Adaptive COSSO & BHAM & SB-GAM & spikeSlabGAM \\ 
  \hline
Binomial &   4 & 0.18 (0.04) & 3.16 (1.39) & 5.51 (4.07) & 2.73 (0.22) & 347.17 (89.43) & 8.41 (0.91) \\ 
  Binomial &  10 & 3.46 (11.06) & 8.30 (1.70) & 10.66 (5.30) & 4.08 (0.29) & 539.05 (135.55) & 20.36 (2.16) \\ 
  Binomial &  50 & 660.31 (141.53) & 103.41 (20.00) & 118.82 (18.45) & 14.22 (0.58) & 1590.09 (142.19) & 236.73 (14.83) \\ 
  Binomial & 100 & - & 662.61 (125.00) & 672.65 (185.09) & 31.61 (2.56) & 2720.53 (250.43) & 967.97 (186.85) \\ 
  Binomial & 200 & - & 5325.66 (995.60) & 4963.93 (1482.11) & 82.17 (3.29) & 4788.76 (420.64) & 3371.88 (194.02) \\ 
  Gaussian &   4 & 0.05 (0.01) & 0.75 (0.09) & 0.75 (0.11) & 8.78 (1.57) & 38.82 (2.74) & 1.84 (0.18) \\ 
  Gaussian &  10 & 0.32 (0.39) & 3.42 (0.24) & 3.41 (0.23) & 20.77 (3.95) & 76.12 (5.55) & 5.93 (0.57) \\ 
  Gaussian &  50 & 72.03 (57.99) & 33.98 (2.88) & 34.35 (2.86) & 285.73 (12.53) & 374.76 (23.79) & 65.18 (8.12) \\ 
  Gaussian & 100 & - & 117.79 (3.33) & 119.63 (3.66) & 372.01 (56.92) & 640.44 (21.91) & 194.14 (8.09) \\ 
  Gaussian & 200 & - & 518.86 (40.78) & 524.76 (39.15) & 471.46 (72.23) & 1300.70 (72.74) & 738.52 (62.76) \\ 
   \hline
\end{tabular}
\caption{The average and standard deviation of computation time in seconds,
      including cross-validation and final model fitting, over 50 iterations. The models
      of comparison include the proposed Bayesian hierarchical additive model (BHAM), the linear LASSO model (LASSO),
      component selection and smoothing operator (COSSO), adaptive COSSO,
      mgcv, sparse Bayesian generalized additive model (SB-GAM), spikeSlabGAM. mgcv doesn't 
      provide estimation whe number of parameters exceeds sample size i.e. p = 100, 200.} 
\label{tab:time_sim}
\end{sidewaystable}
